**Nort East Atlantic Mackerel**

### 2023-02-09 Rmd/condMac.Rmd
conditional; updated

theme_set(theme_bw(16))
```

```{r, eval=FALSE}
source("../R/get_dropbox.R")
```

```{r}
matFn<-function(wt,x) 
   1/(1+exp(-x[1]*(wt-x[2])))
```

```{r, dbox}
dropboxdir<-try(file.path(get_dropbox(), "pelagics"))
if ("try-error"%in%is(dropboxdir))
  dropboxdir="~/Dropbox/pelagics"
```

@@

```{r, mac.data}
load(file.path(dropboxdir,"data/om/mac.RData"))
ts =as.data.frame(read_excel(file.path(dropboxdir,"data/inputs/dat.xlsx"),3))
wt =transform(as.data.frame(stock.wt(mac),drop=TRUE),cohort=year-as.numeric(age))
wt =merge(wt,ts,by="year")
wt=ddply(wt,.(age), transform, rsdl =data/mean(data))
wt=ddply(wt,.(age), transform, rsdl_=rsdl/var(data)^0.5)
wt$age=factor(wt$age,levels=sort(unique(wt$age)))

@@

@@

```{r, mac.m, fig.width=8,fig.height=4}
ggplot(mat)+  
  geom_line(aes(year,data,group=cohort),linetype=3,colour="grey10")+ 
  geom_line(aes(year,data,group=age,col=age))+
  geom_point(aes(year,data,col=age))+
  xlab("Year")+ylab("Mass-at-age")+
  theme(legend.position="bottom")+
  scale_color_manual("Age",values=rainbow(length(unique(wt$age))))
```

@@

```{r, mac.mat, fig.width=8,fig.height=4}
ggplot(m)+  
  geom_line(aes(year,data,group=cohort),linetype=3,colour="grey10")+ 
  geom_line(aes(year,data,group=age,col=age))+
  geom_point(aes(year,data,col=age))+
  xlab("Year")+ylab("Mass-at-age")+
  theme(legend.position="bottom")+
  scale_color_manual("Age",values=rainbow(length(unique(wt$age))))
```

@@

```{r, mac.mat2, fig.width=8,fig.height=5}
#wt$age=factor(wt$age,levels=rev(levels(wt$age)))
#ggbivariate(subset(wt,rsdl<5&rsdl>0), outcome="data", explanatory=c("age", "tb"))
a=ggplot(mat)+
  geom_boxplot(aes(age,data))+
  xlab("Mass-at-age")+ylab("Age")
b=ggplot(mat)+
  geom_point(aes(tb,rsdl))+
  geom_smooth(aes(tb,rsdl),method="lm")+
  facet_wrap(age~.)+
  xlab("Biomass")+ylab("Residual")
ggarrange(a,b ,label.y=1,  
          widths = c(4,6), heights = c(1,1,1),
          nrow   = 1,          ncol    = 2)+
  theme_bw(16)+
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank())
```

>>>>

theme_set(theme_bw(16))

source("../R/get_dropbox.R")

matFn<-function(wt,x) 
   1/(1+exp(-x[1]*(wt-x[2])))

dropboxdir<-try(file.path(get_dropbox(), "pelagics"))
if ("try-error"%in%is(dropboxdir))
  dropboxdir="~/Dropbox/pelagics"

```

@@

```{r, mac.data}

load(file.path(dropboxdir,"data/om/mac.RData"))
ts =as.data.frame(readxl::read_excel(file.path(dropboxdir,"data/inputs/dat.xlsx"),sheet="ts"))
wt =transform(as.data.frame(stock.wt(mac),drop=TRUE),cohort=year-as.numeric(age))
wt =merge(wt,ts,by="year")
wt=ddply(wt,.(age), transform, rsdl =data/mean(data))
wt=ddply(wt,.(age), transform, rsdl_=rsdl/var(data)^0.5)
wt$age=factor(wt$age,levels=sort(unique(wt$age)))

@@

\newpage

@@

\newpage

```{r, mac.m, fig.width=8,fig.height=4}
ggplot(mat)+  
  geom_line(aes(year,data,group=cohort),linetype=3,colour="grey10")+ 
  geom_line(aes(year,data,group=age,col=age))+
  geom_point(aes(year,data,col=age))+
  xlab("Year")+ylab("Maturity-at-age")+
  theme(legend.position="bottom")+
  scale_color_manual("Age",values=rainbow(length(unique(wt$age))))
```

@@

\newpage

```{r, mac.mat, fig.width=8,fig.height=4}
ggplot(m)+  
  geom_line(aes(year,data,group=cohort),linetype=3,colour="grey10")+ 
  geom_line(aes(year,data,group=age,col=age))+
  geom_point(aes(year,data,col=age))+
  xlab("Year")+ylab("M-at-age")+
  theme(legend.position="bottom")+
  scale_color_manual("Age",values=rainbow(length(unique(wt$age))))
```

@@

\newpage

```{r, mac.mat2, fig.width=8,fig.height=5}
#wt$age=factor(wt$age,levels=rev(levels(wt$age)))
#ggbivariate(subset(wt,rsdl<5&rsdl>0), outcome="data", explanatory=c("age", "tb"))
a=ggplot(mat)+
  geom_boxplot(aes(age,data))+
  xlab("Maturity-at-age")+ylab("Age")
b=ggplot(mat)+
  geom_point(aes(tb,rsdl))+
  geom_smooth(aes(tb,rsdl),method="lm")+
  facet_wrap(age~.)+
  xlab("Biomass")+ylab("Residual")
ggarrange(a,b ,label.y=1,  
          widths = c(4,6), heights = c(1,1,1),
          nrow   = 1,          ncol    = 2)+
  theme_bw(16)+
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank())
```
